---
title: 'Part 1: Stringr Functions'
author: "Katelin Seeto"
date: "2/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # contains stringr
```

### Detect string patterns with `str_detect()`
* function to search for a pattern you provide in the variable you specify for any entry that matches that pattern  
* looks for exact match to pattern and returns TRUE or FALSE (a logical) for each element  
* `str_subset()` wraps `filter()` and `str_detect()` into one function

```{r}
# Create toy vector (for this example) that contains a number of different strings 
# Add whitespaces to see how stringr can deal with that too
vec <- c("A Unicorn   Fish ", "add   cornmeal", "French FRIES", "acorn Squash ")


# Which of these strings in the vector contain the word "corn"?
str_detect(vec, pattern = "corn")


#What if we're searching in a df? 
# view(starwars)

# Want to detect in starwars df if the string "walk" shows up
# Will put inside a filter() to keep rows where pattern does show up 
walk_subset <- starwars %>% 
  filter(str_detect(name, pattern = "walk"))

#`str_subset` does same as above but with one function 
fin_subset <- str_subset(starwars$name, pattern = "Fin")

``` 
### Replace a string pattern with something else using `str_replace()`
* For example if a spp name has been misspelled throughout a whole dataset
```{r}
# create a new vector from toy vector where anytime "corn" shows up replace it with "COOL"
vec_bren <- str_replace(vec, pattern = "corn", replacement = "COOL")

vec_bren

# in df, replace the pattern "Sky" with the pattern "TORNADO"
sw_tornado <- starwars %>% 
  mutate(name = str_replace(name, pattern = "Sky", replacement = "TORNADO"))
```

