---
title: 'Part 2: Text Analysis with The Hobbit'
author: "Katelin Seeto"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytext)
library(textdata)
library(pdftools)
library(ggwordcloud)
```

### Read in The Hobbit with `pdftools::pdf_text()` since text is in pdf format
* When you open that text notice that line separation is shown by \n
* Each page of text doc is stored its own element inside a huge vector containing all the text. 
* Ex) page 34 is 34th element
```{r, cache = TRUE}

hobbit_text <- pdf_text("the-hobbit.pdf")

# Since file is large and it take a long time to run function we don't want this too run every time we knit
# add cache = TRUE to code chunk header so it won't re-run that code when you're knitting unless a change has been made to the code 
```

### Search for text on page 34 
```{r}
hobbit_text_p34 <- hobbit_text[34]
hobbit_text_p34

# Notice it's still not tidy

```

### Take entire text, split it up by line, then trim excess whitespace 
* Use `str_split()` to recognize anywhere there is a line break (\n) and split that up and then un-nest them into their own. Must write out as "\\n" since \ tells R that it should recognize what's coming next as a character, don't assume it's something else
* `unnest()` to take each element of each vector and give it it's own space 
```{r}
hobbit_tidy <- data.frame(hobbit_text) %>%  #convert hobbit text into df, each row is now a page
  mutate(text_full = str_split(hobbit_text, pattern = '\\n')) %>%  # text_full contains a series of strings which is each line but is still only part of same element
  unnest(text_full) %>% # hobbit_text is chapter info but now each line of text, has it's own line in df in the text_full col
  mutate(text_full = str_trim(text_full)) #remove whitespace

```

### Wrangle so that there is grouping variable that indicates the chapter number so we can do analysis comparing differt chapters 
* use `str_detect()` to detect the word "chapter"
* Will create a new column to list chapter and will duplicate for when "Chapter" appears but will list NA if it doesn't 
* use mutate(chapter = case_when()) since it will be a conditional column
* must specify what class is associated with your NA values in this column, in this case NA_character
* then will use `fill()` to fill in that chapter number to any NA's below it until it gets to next non-NA value
```{r}
hobbit_df <- hobbit_tidy %>% 
  slice(-(1:125)) %>% # remove title pg, table contents etc
  mutate(chapter = case_when(
    str_detect(text_full, pattern = "Chapter") ~ text_full, 
    TRUE ~ NA_character_
  )) %>% 
  fill(chapter)
```











